\begin{tcolorbox}[colframe=black, colback=white, sharp corners, boxrule=1pt, width=\textwidth]
    \begin{center}
        {\Large \textbf{SWOT Analysis of Mobile-CMUNeXt}}
    \end{center}

    \begin{minipage}{0.48\textwidth}
        \textbf{Strengths}
        \begin{itemize}
            \item \textbf{Low computational complexity}: Achieved through lightweight model architecture and quantization.
            \item \textbf{Real-time inference with FPGAs}: Future FPGA implementation will ensure efficient execution.
            \item \textbf{Optimized quantization techniques}: Initial experiments have successfully reduced precision while maintaining accuracy.
            \item \textbf{Energy-efficient for edge devices}: The model is designed for resource-constrained environments, making it suitable for real-world medical applications.
        \end{itemize}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \textbf{Weaknesses}
        \begin{itemize}
            \item \textbf{FPGA-specific optimizations required}: Hardware-aware adjustments are necessary to maximize efficiency.
            \item \textbf{Limited support for high-precision tasks}: The quantization process may reduce segmentation accuracy for small or complex structures.
            \item \textbf{Trade-off between accuracy and efficiency}: A fine balance must be achieved to ensure that performance is not compromised by aggressive model compression.
        \end{itemize}
    \end{minipage}
    \vspace{0.5cm}
    
    \begin{minipage}{0.48\textwidth}
        \textbf{Opportunities}
        \begin{itemize}
            \item \textbf{Integration into low-power medical devices}: The lightweight nature of Mobile-CMUNeXt makes it ideal for embedded medical systems.
            \item \textbf{Expansion into real-time healthcare applications}: FPGA acceleration will enable deployment in time-sensitive medical workflows.
            \item \textbf{Potential for further model compression}: Additional techniques such as mixed-precision quantization and weight pruning could further optimize efficiency.
        \end{itemize}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \textbf{Threats}
        \begin{itemize}
            \item \textbf{Competition with GPU-based solutions}: FPGA implementations must match or exceed GPU performance to be widely adopted.
            \item \textbf{Hardware compatibility challenges}: Selecting and optimizing for a specific FPGA board may introduce limitations.
        \end{itemize}
    \end{minipage}
\end{tcolorbox}